\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-14 paper.tex
Simplify the abstract

\maketitle
\section*{\normalsize\textbf{Abstract}}
Data as a Service (DaaS) has been offering consumption data, geographic information, etc., for a number of years and has evolved into a multi-billion dollar industry. But IoT cannot be considered a mere extension of DaaS. Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled data marketplaces, trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.

In this paper, we propose a novel approach to construct IoT-enabled data marketplace by means of decentralized and trustless architecture, posting the trade records but also including the transaction process on the distributed ledgers. This way can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain. In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of the device, simultaneously making a verifiable Auth-compliant request to the platform. Later, the verified data will enter the data marketplace to be traded. Furthermore, the platform will complete matching, trading and refunding process without the human intervention which also protects the rights of data providers and consumers through a trading policy written on the smart contract, and finally apply evolutionary game theory to the machine economy.

\begin{IEEEkeywords}
    streaming data, crowd sensing, data marketplace, decentralization
\end{IEEEkeywords}

>>>>

\maketitle
\section*{\normalsize\textbf{Abstract}}
Transacting IoT data must be different in many respects to build much-needed trust in data marketplaces, trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making. In this paper, we propose a novel approach to construct IoT-enabled data marketplace by decentralized and trustless architecture, posting the trade records but also including the transaction process on the distributed ledgers. It can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain. Storage via an end-to-end encrypted message channel allows emitting and accessing trusted data stream over the distributed ledgers regardless of the size or cost of the device, simultaneously making a verifiable Auth-compliant request to the platform. Furthermore, the platform will complete matching, trading and refunding process without the human intervention which also protects the rights of data providers and consumers through a trading policy written on the smart contract, and finally apply evolutionary game theory to the machine economy.
\begin{IEEEkeywords}
    streaming data, crowd sensing, data marketplace, decentralization
\end{IEEEkeywords}
